{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-05 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, wu yeee

        \end{theorem}
        We introduce two examples variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.  
    \section{Algorithms formulations of GMAPG}
        MFISTA by Beck is an example of Definition \ref{def:generic-mapg-ls}. 
        % ======================================================================
        % EXAMPLE | MFISTA WITH ARMIJO LINE SEARCH
        % ======================================================================
        \begin{algorithm}[H]
            \begin{algorithmic}[1]
                \STATE{\textbf{Input:}}
                \caption{Armijo Line Search}
            \end{algorithmic}
        \end{algorithm}
        We will now give an algorithimic description of GMAPG. 
        \begin{algorithm}[H]\label{alg:chambolle-btls}
            \begin{algorithmic}[1]
                \STATE{\noindent
                    \textbf{Input:}
                    $f, g, x, v, L> L_{\min} > 0, \rho, \alpha$
                }
                \STATE{$L^+ := \max(L_{\min}, \rho L)$.}
                \FOR{$i = 1, 2, \ldots, 53$}
                    \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + L/L^+} - \alpha^2\right)$. }
                    \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+) x$. }
                    \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$.}
                    \IF{$2D_f(x^+, y^+) \le \Vert x^+ - y^+\Vert^2$}
                        \STATE{\textbf{break}}
                    \ENDIF
                    \STATE{$L^+ := 2^iL^+$.}
                \ENDFOR
                \STATE{\textbf{Return: }$y^+, x^+, \alpha^+, L^+$}
                \caption{Chambolle's Backtracking}
            \end{algorithmic}
        \end{algorithm}

        \begin{algorithm}[H]\label{alg:mfista-chambolle-ada}
            \begin{algorithmic}[1]
                \STATE{\noindent
                    \textbf{Input:} $f, g, x_{-1}, L_0, r_{\min}, \text{Exit condition: }\mathbb E_\chi$. 
                }

@@

@@

        \begin{example}[Nesterov's monotone scheme with generic line search]\;\\\vspace{-1em}
            \begin{algorithm}\label{alg:nesterov-mono-generic-ls}
            \begin{algorithmic}[1]
            \STATE{\textbf{Input: } }
            \end{algorithmic}\caption{Nesterov's monotone scheme with generic line search}
            \end{algorithm}
        \end{example}

    \section{Practical enhancement}
        In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
    \section{Restarting with gradient and function values}

>>>>

        We introduce two examples variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.  
    \section{Algorithmic description of GMAPG}
        There are several components to the GMAPG algorithm. 
            \begin{algorithmic}[1]\label{alg:armijo-ls}
                \STATE{\textbf{Function ArmijoLS}
                    $(f, g, x, v, L, \alpha, \_, \_)$
                \caption{Armijo Line Search}
        \begin{algorithm}[H]\label{alg:chambolle-btls}
                    \textbf{Function ChambBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
                \STATE{$L^+ := \max(L_{\min}, \rho L)$.}
                \FOR{$i = 1, 2, \ldots, 53$}
                    \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + L/L^+} - \alpha^2\right)$. }
                    \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+) x$. }
                    \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$.}
                    \IF{$2D_f(x^+, y^+) \le \Vert x^+ - y^+\Vert^2$}
                        \STATE{\textbf{break}}
                    \STATE{$L^+ := 2^iL^+$.}
                \STATE{\textbf{Return: }$y^+, x^+, \alpha^+, L^+$}
                \caption{Chambolle's Backtracking}
        \begin{algorithm}[H]\label{alg:beck-mono}
                    \textbf{Function BeckMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)
                \caption{Beck's monotone routine}
        \begin{algorithm}[H]\label{alg:nes-mono}
                    \textbf{Function NesMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)
                \caption{Nesterov's monotone routine}
        \begin{algorithm}[H]\label{alg:gmapg}
                    \textbf{Function GMAPG} (
                        $f, g, x_{-1}, L_0, r_{\min}, \text{Exit condition: }\mathbb E_\chi$

@@

    % SECTION | EXAMPLES OF GMAPG IN THE LITERATURE
    \section{Examples of GMAPG in the literature}

@@

        \begin{example}[Nesterov's monotone scheme with generic line search]\;\\\vspace{-1em}
            \begin{algorithm}\label{alg:nesterov-mono-generic-ls}
            \STATE{\textbf{Input: } }
            \end{algorithmic}\caption{Nesterov's monotone scheme with generic line search}

    \section{Practical enhancement}
        In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
    \section{Nonconvex convergence}

    \section{Restarting with gradient and function values}
